MCC Kids Model Predictions

### 2018-11-28 stats/kids/kids_model_predictions.Rmd
kids model predictions update

pref_post_same<- webppl(
  program_code = paste(rsaUtils, rsaModel, postPrefWebppl , sep='\n'),
  data = pref_data%>%filter(condition == "same_speaker")%>%mutate(minage = min(age_num)), 
  data_var = "dataFromR",
  model_var = "model",
  chains = 3,
  cores = 3,
  inference_opts = list(method = "MCMC", samples = 2000, burn = 200, verbose = T)
)

## MH sketching

```{r}
postPrefConWebppl <- '

@@

var priorProbs = []

@@

    var speakerOptimality = so_int  + so_slope * (age - infData[0].minage)
    var inf_priorProbs = [.5, .5, .5]

@@

  var pref_params = map(function(cndtn){
    var conditionData = filter(prefData, {condition: cndtn})

@@

    var diff_priorProbs_congruent = [1-priorReg, 1-priorReg, priorReg]
    var diff_priorProbs_incongruent = [priorReg, priorReg, 1-priorReg]

@@

      ...

@@

    ...

    return extend(diff_speaker_params, same_speaker_params, {
      diff_priorReg,
      same_priorReg,
      speakerOptimality,
      rsaPredictions_diff_cong,
      rsaPredictions_diff_incong,
      rsaPredictions_same_cong,
      rsaPredictions_same_incong,
      age_bin,
      so_slope,
      so_int
    })

@@

```{r}
postSoWebppl <- '

>>>>

```{r}
modelPredWebppl <- '

@@

//var priorProbs = []

@@

var inf_priorProbs = [.5, .5, .5]

@@

  var pref_params = map(function(cndtn){

    var conditionData = filter(prefData, {condition: cndtn})

@@

    var diff_priorProbs_congruent = [1-diff_priorReg, 1-diff_priorReg, diff_priorReg]

    var diff_priorProbs_incongruent = [diff_priorReg, diff_priorReg, 1-diff_priorReg]

@@

  var rsaPredictions_diff_incong = expectation(pragmaticListener({label: "dax", point: 2 }, diff_priorProbs_incongruent, speakerOptimality))

@@

    var same_priorProbs_congruent = [1-same_priorReg, 1-same_priorReg, same_priorReg]

    var same_priorProbs_incongruent = [same_priorReg, same_priorReg, 1-same_priorReg]

  var rsaPredictions_same_cong = expectation(pragmaticListener({label: "dax", point: 2 }, same_priorProbs_congruent, speakerOptimality))

  var rsaPredictions_same_incong = expectation(pragmaticListener({label: "dax", point: 2 }, same_priorProbs_incongruent, speakerOptimality))

    return extend(
    //diff_speaker_params, same_speaker_params, 
{
     // diff_priorReg,
    //  same_priorReg,
    //  speakerOptimality,
      rsaPredictions_diff_cong,
      rsaPredictions_diff_incong,
      rsaPredictions_same_cong,
      rsaPredictions_same_incong,
      age_bin,
    //  so_slope,
    //  so_int
    })

@@

```{r combined model predictions}
model_pred<- webppl(
  program_code = paste(rsaUtils, rsaModel, modelPredWebppl , sep='\n'),
  data = pre_data, 
  data_var = "dataFromR",
  model_var = "model",
  chains = 1,
  cores = 1,
  inference_opts = list(method = "MCMC", samples = 20, burn = 1, verbose = T)
)
